Making Sense of Tweets: Student research projects in data science

### 2019-09-08 Rmd/abstract.Rmd
elaborated abstract

Social media platforms have altered the way that we communicate. The tremendous volumes of streaming data that are available through platforms like Twitter and Facebook enable the investigation of new data science research questions. In many cases, these research questions may serve as engaging and scientifically meaningful studies for those who are new to data science research. 
In seeking to explore social media data science as a pedagogical tool, we guided two undergraduate researchers during the 2015-2016 academic year while they completed mentored research projects.

>>>>

Social media platforms have altered the ways that we communicate. The tremendous volumes of streaming data that are available through platforms like Twitter and Facebook enable the investigation of new data science research questions. In many cases, these research questions may motivate engaging, accessible, and scientifically meaningful studies for those who are new to data science research. 
In seeking to explore social media data science as a pedagogical tool, we guided two undergraduate researchers during the 2015-2016 academic year while they completed research projects. After discussing the nature of downloaded Twitter data, we encouraged the students to formulate novel research questions that both  draw on the time series structure of tweets and complement students' existing data science interests. One student elected to study relationships over time between tweet sentiments and stock market index values. The other chose to develop methods for using tweets to detect social media events, like the occurrence of the Super Bowl football game.
